A Classical Density-Functional Theory for Describing Water Interfaces

### 2012-08-14 papers/water-SAFT/paper.tex

A number of classical density functionals have been developed for
water~\cite{ding1987, Yang1992, yang1994density, gloor2002saft, 
  gloor2004accurate, gloor2007prediction, Jaqaman2004, clark2006developing,
  lischner2010classical, fu2005vapor-liquid-dft,kiselev2006new,
  blas2001examination}, each of which
captures some of the qualitative behavior of water.  However, each of
these functionals also fail to capture some of water's unique
properties.  For instance, the functional of Lischner \emph{et
  al}\cite{lischner2010classical} treats the surface tension
correctly, but can only be used at room temperature, and thus captures
none of the temperature-dependence of water.  A number of classical
density functionals have recently been produced that are based on
Statistical Associating Fluid Theory (SAFT)\cite{ 
  yu2002fmt-dft-inhomogeneous-associating,
  fu2005vapor-liquid-dft,gloor2002saft,muller2001molecular,
  clark2006developing, gloor2007prediction, gloor2004accurate,
  gross2009density, kahl2008modified, blas2001examination}.  These
functionals are based on a perturbative thermodynamic expansion, and
do reproduce the temperature-dependence of water's properties.

@@

%% \begin{table}
%% \begin{tabular}{|c|c|c|c|c|}
%% \hline
%% paper & SAFT functional & water & LDA & tension \\
%% \hline
%% yuwu2002dft & X & & & \\
%% \hline
%% fuwu2005 & X & X & & X \\
%% \hline
%% kiselev2006 &  & X & X & X \\
%% \hline
%% clark2006developing & X & X & X & X \\
%% \hline
%% gloor2002 & X & X & X & X \\
%% \hline
%% gloor2004 & X & X & X & X \\
%% \hline
%% gloor2007 & X & X & X & X \\
%% \hline
%% gross2009 & X &  & X & X \\
%% \hline
%% Lischner2010 &  & X &  &  \\
%% \hline
%% Blas2001 & X & X & X & X \\
%% \hline
%% Kahl2008 & X &  & X & X \\
%% \hline
%% Muller2001 & X &  &  &  \\
%% \hline
%% Yang1994 &  & X &  & X \\
%% \hline
%% ding1987 &  & X & ? &  \\
%% \hline
%% Jaqaman2004 &  & X & ? & X \\
%% \hline
%% next & ? & ? & ? & ? \\
%% \hline
%% \end{tabular}
%% \caption{Which papers do what}
%% \end{table}

>>>>

A number of classical density functionals have been developed for
water~\cite{ding1987, Yang1992, yang1994density, gloor2002saft, 
  gloor2004accurate, gloor2007prediction, Jaqaman2004, chuev2006, clark2006developing,
  lischner2010classical, fu2005vapor-liquid-dft,kiselev2006new,
  blas2001examination}, each of which
captures some of the qualitative behavior of water.  However, each of
these functionals also fail to capture some of water's unique
properties.  For instance, the functional of Lischner \emph{et
  al}\cite{lischner2010classical} treats the surface tension
correctly, but can only be used at room temperature, and thus captures
none of the temperature-dependence of water.  A number of classical
density functionals have recently been produced that are based on
Statistical Associating Fluid Theory (SAFT)\cite{ 
  yu2002fmt-dft-inhomogeneous-associating,
  fu2005vapor-liquid-dft,gloor2002saft,muller2001molecular,
  clark2006developing, gloor2007prediction, gloor2004accurate,
  gross2009density, kahl2008modified, blas2001examination}.  These
functionals are based on a perturbative thermodynamic expansion, and
do reproduce the temperature-dependence of water's properties.

@@

%% \begin{table}
%% \begin{tabular}{|c|c|c|c|c|}
%% \hline
%% paper & SAFT functional & water & LDA & tension \\
%% \hline
%% chuev2006 &  & X &  & X \\
%% \hline
%% yuwu2002dft & X & & & \\
%% \hline
%% fuwu2005 & X & X & & X \\
%% \hline
%% kiselev2006 &  & X & X & X \\
%% \hline
%% clark2006developing & X & X & X & X \\
%% \hline
%% gloor2002 & X & X & X & X \\
%% \hline
%% gloor2004 & X & X & X & X \\
%% \hline
%% gloor2007 & X & X & X & X \\
%% \hline
%% gross2009 & X &  & X & X \\
%% \hline
%% Lischner2010 &  & X &  &  \\
%% \hline
%% Blas2001 & X & X & X & X \\
%% \hline
%% Kahl2008 & X &  & X & X \\
%% \hline
%% Muller2001 & X &  &  &  \\
%% \hline
%% Yang1994 &  & X &  & X \\
%% \hline
%% ding1987 &  & X & ? &  \\
%% \hline
%% Jaqaman2004 &  & X & ? & X \\
%% \hline
%% next & ? & ? & ? & ? \\
%% \hline
%% \end{tabular}
%% \caption{Which papers do what}
%% \end{table}
